### 2017-01-02 paper/evaluation.tex
fixed execution order

\newcommand{\SubjCnt}{412}

A Maven project may contain several submodules with multiple
\emph{pom.xml} files. We considered only projects with a
\emph{pom.xml} file located in the root directory.  As of December
30th 2016, our search criteria returned 615 subjects. From the 615
downloaded projects, 46 were not Maven projects, 26 were unable to
fetch all dependencies (\eg, due to the usage of a private library),
and 131 were in an unstable revision. Our final set consists in
\SubjCnt{} subjects.

@@

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
(64-bit version). Software settings include \Comment{the Linux
\emph{sysstat} package to measure performance, }\emph{git} to fetch
subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test subjects,
and \emph{Python 3.4} to run our evaluation scripts. For replication,
all source artifacts are publicly available at \Fix{create gh-pages},
including supporting scripts (\eg, the script that test subjects and
generates the raw data), the full list of projects, and a
\emph{Vagrantfile} to emulate our hardware and all software
dependencies.

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \SubjCnt{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our scripts
to test each subject. The main loop (line 12) iterates over the list
of subjects and invokes the wrapper function \emph{run} to execute
Maven in separated steps (lines 14-16). To avoid inflating the
measured time, we first fetch all dependencies (line 14), compile the
source and test files (line 15) and later, we invoke Maven in offline
mode (line 16) to avoid package updates. In addition we randomly
selected 100 Maven logs to inspect and identify non-related tasks
(\eg, \emph{javadoc} generation and static analysis). We created a
list of plugins (lines 1-5) to ignore them during the test execution.
After the test execution, we use a simple regular expression over the
builder output to extract the elapsed time.

@@

for subject in SUBJECTS:
   os.chdir(subject)
   run(["mvn", "dependency:go-offline"])
   run(["mvn", "clean", "install", "-DskipTests"])
   run(["mvn", "-o", "test"], MAVEN_IGNORES)
\end{lstlisting}
\caption{\label{fig:mvn-execution} Python script to evaluate the
    time cost of test suites. For each subject, we fetch all
    dependencies, compile the source and test files, and execute the
    tests in offline mode ignoring non-related tasks.}
\end{figure}

We grouped the subjects according to the execution time: tests that
ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{medium execution}), and more than five minutes
(\emph{long execution}). Figure~\ref{fig:piechart-time} shows the
proportion of subjects per group and Figure~\ref{fig:boxplots-time}
shows the distribution of elapsed time for each group (boxplots).

>>>>

\newcommand{\SubjCnt}{411}

A Maven project may contain several submodules with multiple
\emph{pom.xml} files. We considered only projects with a
\emph{pom.xml} file located in the root directory.  As of December
30th 2016, our search criteria returned 615 subjects. From the 615
downloaded projects, 46 were not Maven projects, 27 were unable to
fetch all dependencies (\eg, due to the usage of a private library),
and 131 were in an unstable revision. Our final set consists in
\SubjCnt{} subjects.

@@

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
(64-bit version). Software settings include \Comment{the Linux
\emph{sysstat} package to measure performance, }\emph{git} to fetch
subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test subjects,
and \emph{Python 3.4} to run our evaluation scripts. For replication,
all source artifacts are publicly available at \Fix{create gh-pages},
including supporting scripts (\eg, the script that test subjects and
generates the raw data), and the full list of projects. \Comment{, and a
\emph{Vagrantfile} to emulate our hardware and all software
dependencies.}

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \SubjCnt{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our scripts
to test each subject. The main loop (line 12) iterates over the list
of subjects and invokes the wrapper function \emph{run} to execute
Maven in separated steps (lines 14-16). To avoid inflating the
measured time, we first compile the source and test files (line 14),
fetch all dependencies (line 15) and later, we run the tests in offline
mode (line 16) to avoid package updates. In addition we randomly
selected 100 Maven logs to inspect and identify non-related tasks
(\eg, \emph{javadoc} generation and static analysis). We created a
list of plugins (lines 1-5) to ignore them during the test execution.
Finally, we use a simple regular expression over the test output to
extract the elapsed time.

@@

for subject in SUBJECTS:
   os.chdir(subject)
   run(["mvn", "clean", "install", "-DskipTests"])
   run(["mvn", "dependency:go-offline"])
   run(["mvn", "-o", "test"], MAVEN_IGNORES)
\end{lstlisting}
\caption{\label{fig:mvn-execution} Python script to evaluate the time cost of
    test suites. For each subject, we compile the source and test files, fetch
    all dependencies, and execute the tests in offline mode ignoring
    non-related tasks.}
\end{figure}

We grouped the subjects according to the execution time: tests that
ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{medium execution}), and more than five minutes
(\emph{long execution}). A previous work used a similar categorization
except for the \emph{medium} group \cite{gligoric-etal-issta2015}.  We
added a new group because \Fix{justify or use the same
classification}.  Figure~\ref{fig:piechart-time} shows the proportion
of subjects per group and Figure~\ref{fig:boxplots-time} shows the
distribution of elapsed time for each group (boxplots).
